\bf Faster Neural Machine Translation Inference

### 2018-05-11 fast-beam/fast-beam.tex
use requireProb

Secondly, we are only interested in the probabilities of the best classes. Since they are now known at the start of the kernel, we compute softmax only for those classes. The outline of the our function is shown in Algorithm~\ref{algo:Fused Kernel}.

@@

\Comment{calculate denominator}

\State $sum \gets 0$ 
\ForAll{$p_i$ in $p$}
  \If{$p_i > max$}
    \State $sum \gets sum + \exp(p_i - max)$
  \EndIf
\EndFor

@@

Thirdly, calculation of $max$ and $sum$ can be done in one loop by adjusting the sum whenever a higher $max$ is found, Equation~`.
\begin{eqnarray*}
sum & = & e^{a - max_b} + e^{b - max_b} \\
    & = & e^{a - max_a + \Delta} + e^{b - max_b} \\
    & = & e^{\Delta} e^{a - max_a} + e^{b - max_b}
\end{eqnarray*}
where $\Delta = max_b - max_a$ and $max_b > max_a$.

@@

>>>>

Secondly, we are only interested in the probabilities of the best classes. Since they are now known at the start of the kernel, we compute softmax only for those classes.

@@

\State $max \gets - \infty$ 
\State $sum \gets 0$

\ForAll{$p_i$ in $p$}
  \State $p_i' \gets p_i + b_i$  
  \If{$p_i' > max$}
    \State $\Delta \gets max - p_i'$
    \State $sum \gets \Delta \times sum + 1 $
    \State $max \gets p_i'$
    \State $best \gets i$
  \Else
    \State $sum \gets sum + \exp(p_i' - max)$
  \EndIf
\EndFor

@@

Thirdly, the calculation of $max$ and $sum$ can be done in one loop by adjusting $sum$ whenever a higher $max$ is found, Equation~`.
\begin{eqnarray*}
sum & = & e^{a - max_b} + e^{b - max_b} \\
    & = & e^{a - max_a + \Delta} + e^{b - max_b} \\
    & = & e^{\Delta} e^{a - max_a} + e^{b - max_b}
\end{eqnarray*}
where $\Delta = max_a - max_b$ and $max_b > max_a$. The outline of the our function is shown in Algorithm~\ref{algo:Fused Kernel}.

@@

This changes does not reduce the asymtotic runtime of our algorithm which remains at $\mathcal{O}(|p|)$, it brings the number of iterations over $p$ down from 5 to 1. In practise, this has a significant affect on inference speed.
